\clearpage
\section*{Response to Reviewers}

Thank you for your thorough review of the previous version of this article.


\subsection*{Response to Reviewer \#1}

\review{I think authors have responded to all my previous requests with sufficient revision, and as a result, the paper is much easier to read and comprehend. I liked the technical contribution, to begin with, and the updated representation means I am now happy to see this accepted.}

Thank you again for taking the time to review the paper and suggesting useful changes.



\subsection*{Response to Reviewer \#2}

\review{However, results would be more useful if there was an analysis of the characteristics of problems, and why the proposed method works on these particular problems, instead of only claiming superiority.}

This is an interesting question, and we have tried hard to find a good answer to this problem. However, from our literature search and ad-hoc experiments, we find that \flash, similar to sequential model-based optimization, is a black box approach and does not make any assumption about the problem space. However, the time when \flash would become ineffective is when the surrogate model (CART in our setting) is not able to model the search space. Empirically we (and other researchers) have found that CART is a good modeling technique, but there may exist some software system which cannot be effectively modeled. 

To take this further, we find that \flash make some assumptions about the problem space, which may not hold true in some practical setting. In this revision, we add a discussion section, where we discuss various shortcomings of \flash and discuss potential solutions to those problems. \citeresp{2-1}